\documentclass[11pt]{article}

\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{framed}
\usepackage{tabularx}
\usepackage{url}

% Add spacing between paragraphs
\setlength{\parskip}{0.5em}
%\setlength{\parindent}{0pt}

\title{SÁL242F Exercise 5: An introduction to Bayesian statistics}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Overview}

In this exercise you will follow the tutorial in the 2025 paper by Alter et al., titled \textit{Navigating the Bayes maze: The psychologist’s guide to
Bayesian statistics, a hands-on tutorial with R code}. The paper is available at \url{https://onlinelibrary.wiley.com/doi/10.1002/ijop.13271}. The tutorial will introduce you to the basics of Bayesian statistics, including how to specify models, choose priors, and interpret results. You will also learn how to use the \texttt{brms} package in R to fit Bayesian models.

\section*{Instructions}

\noindent
Your task is to:
\begin{itemize}
    \item read the paper and follow the tutorial step by step,
    \item run the R code provided in the paper and experiment with it,
    \item try different priors, models, and datasets to see how they affect the results,
    \item note any insights, surprises, or challenges you encounter along the way,
    \item prepare to discuss your observations in class.
\end{itemize}

\noindent
In class, you will present your findings and we will discuss the following questions:
\begin{itemize}
    \item What did you learn about Bayesian statistics from the tutorial?
    \item How do Bayesian methods compare to frequentist methods in terms of interpretation and application?
    \item What are the advantages and disadvantages of using Bayesian statistics in psychological research?
    \item What challenges did you encounter when working with the R code and how did you overcome them?
    \item How can you apply what you learned to your own research projects?
\end{itemize}

\noindent
As always, feel free to use any and all resources at your disposal, including large language models.

\noindent\textbf{Good luck!}

\end{document}